\chapter*{参考文献}
\addcontentsline{toc}{chapter}{参考文献}

\begin{enumerate}
    \item Redmon, J., Divvala, S., Girshick, R., \& Farhadi, A. (2016). You Only Look Once: Unified, Real-Time Object Detection. \textit{CVPR 2016}.
    
    \item Jocher, G., et al. (2023). Ultralytics YOLOv8. \textit{GitHub repository}.
    
    \item Parkhi, O. M., Vedaldi, A., Zisserman, A., \& Jawahar, C. V. (2012). Cats and Dogs. \textit{CVPR 2012}.
    
    \item Howard, A. G., et al. (2017). MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications. \textit{arXiv:1704.04861}.
    
    \item Tan, M., \& Le, Q. V. (2019). EfficientNet: Rethinking Model Scaling for Convolutional Neural Networks. \textit{ICML 2019}.
    
    \item Hinton, G., Vinyals, O., \& Dean, J. (2015). Distilling the Knowledge in a Neural Network. \textit{arXiv:1503.02531}.
    
    \item Woo, S., Park, J., Lee, J. Y., \& Kweon, I. S. (2018). CBAM: Convolutional Block Attention Module. \textit{ECCV 2018}.
    
    \item Schroff, F., Kalenichenko, D., \& Philbin, J. (2015). FaceNet: A Unified Embedding for Face Recognition and Clustering. \textit{CVPR 2015}.
    
    \item He, K., Zhang, X., Ren, S., \& Sun, J. (2016). Deep Residual Learning for Image Recognition. \textit{CVPR 2016}.
    
    \item Lin, T. Y., et al. (2017). Feature Pyramid Networks for Object Detection. \textit{CVPR 2017}.
    
    \item 一般社団法人ペットフード協会 (2023). 令和5年 全国犬猫飼育実態調査.
    
    \item INCOSE (2015). Systems Engineering Handbook: A Guide for System Life Cycle Processes and Activities, 4th Edition.
\end{enumerate}
