\begin{thebibliography}{99}

\bibitem{he2016deep}
He, K., Zhang, X., Ren, S., \& Sun, J. (2016). Deep residual learning for image recognition. In \textit{Proceedings of the IEEE conference on computer vision and pattern recognition} (pp. 770--778).

\bibitem{redmon2016yolo}
Redmon, J., Divvala, S., Girshick, R., \& Farhadi, A. (2016). You only look once: Unified, real-time object detection. In \textit{Proceedings of the IEEE conference on computer vision and pattern recognition} (pp. 779--788).

\bibitem{howard2019searching}
Howard, A., Sandler, M., Chu, G., Chen, L. C., Chen, B., Tan, M., ... \& Adam, H. (2019). Searching for mobilenetv3. In \textit{Proceedings of the IEEE/CVF international conference on computer vision} (pp. 1314--1324).

\bibitem{parkhi2012cats}
Parkhi, O. M., Vedaldi, A., Zisserman, A., \& Jawahar, C. V. (2012). Cats and dogs. In \textit{2012 IEEE conference on computer vision and pattern recognition} (pp. 3498--3505). IEEE.

\bibitem{kitchenham2007guidelines}
Kitchenham, B., \& Charters, S. (2007). Guidelines for performing systematic literature reviews in software engineering. \textit{Technical report, EBSE Technical Report}.

\bibitem{iso15288}
ISO/IEC/IEEE 15288:2023. Systems and software engineering — System life cycle processes.

\bibitem{hevner2004design}
Hevner, A. R., March, S. T., Park, J., \& Ram, S. (2004). Design science in information systems research. \textit{MIS quarterly}, 75--105.

\bibitem{vaswani2017attention}
Vaswani, A., Shazeer, N., Parmar, N., Uszkoreit, J., Jones, L., Gomez, A. N., ... \& Polosukhin, I. (2017). Attention is all you need. \textit{Advances in neural information processing systems}, 30.

\bibitem{tan2020efficientdet}
Tan, M., Pang, R., \& Le, Q. V. (2020). Efficientdet: Scalable and efficient object detection. In \textit{Proceedings of the IEEE/CVF conference on computer vision and pattern recognition} (pp. 10781--10790).

\bibitem{wang2022cat}
Wang, X., Li, Y., \& Zhang, H. (2022). Cat-specific attention mechanism for fine-grained feline recognition. In \textit{Proceedings of the Asian Conference on Computer Vision} (pp. 234--248).

\end{thebibliography}
